PK object batch mode trial

### 2023-10-12 data-raw/Manuscript2023_Workflow.Rmd
Renamed batchMode_trial_gpm.Rmd to Manuscript2023_Workflow.Rmd

# Notes and future directions
- Stratified on species... then chemical class (pharma vs non-pharma, Pharmapendium)
- Classyfier for chemical superclass (talk to Paul) Ranges and Mean for each class...

>>>>

# Preparing results for CvTdb

```{r cvtdb-prep}

my_cvt <- cvt
my_tkstats <- eval_tkstats(my_pk)

my_cvt_unique <- my_cvt %>% dplyr::mutate(
  preprocess_data_flags = 
    case_when(
      (other_study_identifier %in% "S0916") ~ paste("Adjusted dose_level_original_units",
                                                              "adjusted dose_level_normalized.",
                                                              sep = " and "),
      (other_study_identifier %in% "S0624") ~ paste("Adjusted dose_level_normalized."),
      (document_id %in% c("65", "61", "46", "31")) ~ paste("Adjusted analyte_dtxsid",
                                                           "adjusted analyte_name_original.",
                                                           sep = " and "),
      (other_study_identifier %in% c("S0976",
                                     "S0361",
                                     "S0328")) ~ paste("Adjusted loq and loq_units."),
      (document_id %in% "38") ~ paste("Adjusted conc."),
      (analyte_name_original %in% c("n-desmethyltamoxifen",
                                    "methemoglobin")) ~ paste("Adjusted analyte_dtxsid."),
      .default = NA_character_
    )) %>%
  group_by(analyte_dtxsid, species,
    administration_route_normalized, conc_medium_normalized, preprocess_data_flags) %>%
  summarize(document_ids = paste0(unique(document_id), collapse = ","))

# Non-compartmental analysis
my_nca <- get_nca(my_pk) %>% dplyr::select(-param_units) %>%
  mutate(param_name = paste0(param_name, ".nca")) %>%
  group_by(Chemical, Species,
           Route, Media, design) %>%
  pivot_wider(names_from = param_name,
              values_from = c(param_value, param_sd_z)) %>%
  distinct() %>%
  arrange(Chemical) %>%
  rename_with(.fn = ~gsub("param_", "", .x)) %>%
  rename_with(.fn = ~gsub("value_", "", .x)) %>%
  rename(analyte_dtxsid = Chemical,
         species = Species,
         administration_route_normalized = Route,
         conc_medium_normalized = Media)

my_cvt %>%
  dplyr::select(analyte_dtxsid, species, radiolabeled) %>%
  distinct() %>%
  filter(analyte_dtxsid %in% (cvt %>% filter(radiolabeled) %>% pull(analyte_dtxsid)))

# Writing to file
left_join(my_nca, my_cvt_unique) %>%
  ungroup() %>%
  filter(!is.infinite(AUC_infinity.nca), !is.infinite(AUMC_infinity.nca)) %>%
  distinct() %>%
  mutate(nca_id = row_number(),
         .before = analyte_dtxsid) %>% View("NCA-CvTdb")
  # write_tsv("data-raw/NCA_CvTdb.tsv")
# Note that this will have more numbers because it still includes AUC_infinity == NA

# TK stats
my_tkstats <- my_tkstats %>%
  dplyr::select(analyte_dtxsid = Chemical, species = Species,
                administration_route_normalized = Route, 
                conc_medium_normalized = Media, 
                Reference,
                model, method,
                ends_with("tkstats")) %>%
  group_by(across(everything())) %>%
  ungroup(Reference) %>%
  summarize(document_ids = paste0(unique(Reference), collapse = ",")) %>%
  ungroup() %>%
  distinct() %>%
  arrange(analyte_dtxsid)

prefit_df <- my_pk$prefit$fit_check %>% inner_join(get_winning_model(my_pk)) %>%
  dplyr::select(analyte_dtxsid = Chemical, species = Species, model, method, 
                fit_decision, fit_reason)

left_join(my_tkstats, my_cvt_unique) %>%
  left_join(prefit_df) %>%
  ungroup() %>%
  distinct() %>%
  mutate(tkstats_id = row_number(), .before = analyte_dtxsid) %>% View("TKstats-CvTdb")
  # write_tsv("data-raw/tkstats_CvTdb.tsv")
